   \documentclass[12pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{amsmath,amsthm}
\usepackage{fullpage}
\usepackage{amsfonts}
\usepackage{amssymb,multicol}
\usepackage{enumitem}
\usepackage[colorlinks=true]{hyperref}
\usepackage{xcolor}

\newcommand{\Z}{\mathbb{Z}}
\newtheorem*{theorem}{Theorem}

\newlist{checklist}{itemize}{2}
\setlist[checklist]{label=$\square$}

\begin{document}
\begin{center}
{\Large Homework 3}\\
Due: Friday, October 7\\


\end{center}
{\bf Instructions:} Submit a pdf of your solutions to the HW 3 assignment on Gradescope. 

When working on this assignment, you should focus on the following goals:
\begin{itemize}
\item Carefully use and cite the bijection principle.
\item Carefully use and cite the multiplication principle.
\item Use the definitions of combinations and permutations to solve counting problems.
\item Write clear and correct proofs that meet the \href{https://docs.google.com/document/d/18LfQoqi6BsY2VdAlpC5xdYEA2rxSGoH0891nVec4_Os/edit?usp=sharing}{Specifications for a Well-written Solution} with a special focus on the following conventions of a mathematical proof (these are the same as were emphasized in homeworks 1 and 2):
\begin{checklist}
\item Written in complete sentences, taking special care to make sure that equations are included in a sentence. 
\item Defines variables before/when you use them.
\item Uses English words when writing anything besides a mathematical formula or equation (i.e. do not use a symbol, such as $\forall,\, \exists,\, \therefore, \, \text{or }\implies$ in place of a word).
\item No sentences start with a mathematical symbol.
\item Uses symbols when writing a precise mathematical formula or equation.
\item Shows computational/algebraic work vertically and centered in the page. 
\item Tells your reader what you are proving and what you are assuming. 
\item Uses transition words to show the logical connections between sentences and ideas.
\end{checklist}
\end{itemize}

\begin{enumerate}
 \item Let $S_1$, $S_2$, $\ldots$, $S_k$ be finite sets. Using the bijection principle, prove that $$|S_1\times S_2\times\cdots \times S_k|=|(S_1\times S_2\times\cdots\times S_{k-1})\times S_{k}|.$$
\item Complete problem 12 from the Supplementary exercises for Chapter 2 section of the appendix. 

\item Complete problem 32 using the formula in Theorem 4. 
\item Complete {\bf one} of problem 40 or 41. 
\item In as many ways as you can (you may get credit for up to 3 separate proofs), show that $${n\choose k}{n-k\choose m}={n\choose m}{n-m\choose k}.$$
\item Complete problem 10 from the Supplementary exercises for Chapter 3 section of the appendix. 
\end{enumerate}
\end{document}
