   \documentclass[12pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{amsmath,amsthm}
\usepackage{fullpage}
\usepackage{amsfonts}
\usepackage{amssymb,multicol}
\usepackage[colorlinks=true]{hyperref}
\usepackage{ enumitem}
\usepackage{xcolor}

\newcommand{\Z}{\mathbb{Z}}
\newtheorem*{theorem}{Theorem}

\newlist{checklist}{itemize}{2}
\setlist[checklist]{label=$\square$}

\begin{document}
\begin{center}
{\Large MATH 5705: Homework 1}\\
Due: Friday, September 16th at 11:59 pm \\


\end{center}
{\bf Instructions:} Submit a pdf of your solutions to the HW 1 assignment on Gradescope. 

When working on this assignment, you should focus on the following goals:
\begin{itemize}
\item Write a clear proof using induction. 
%\item Carefully use and cite the multiplication principle.
\item Write clear and correct proofs that meet the \href{https://docs.google.com/document/d/18LfQoqi6BsY2VdAlpC5xdYEA2rxSGoH0891nVec4_Os/edit?usp=sharing}{Specifications for a Well-written Solution} with a special focus on the following conventions of a mathematical proof:
\begin{checklist}
\item Written in complete sentences, taking special care to make sure that equations are included in a sentence. 
\item Defines variables before/when you use them.
\item Uses English words when writing anything besides a mathematical formula or equation (i.e. do not use a symbol, such as $\forall,\, \exists,\, \therefore, \, \text{or }\implies$ in place of a word).
\item No sentences start with a mathematical symbol.
\item Uses symbols when writing a precise mathematical formula or equation.
\item Shows computational/algebraic work vertically and centered in the page. 
\end{checklist}
\end{itemize}


\begin{enumerate}

%\item Complete problem 7 from the Supplementary exercises for Chapter 1 section of the appendix. 

\item Carefully prove Versions II and III of Theorem 2 (from the textbook).  You may use Version I in your proofs.  
\end{enumerate}

\end{document}